Detecting threats of violence in YouTube comments

### 2016-02-18 submission.tex
Added abstract

\begin{abstract}
Here comes an abstract for this article
\end{abstract}

@@

@@

>>>>

\begin{abstract}
This article investigates the effect of various types of linguistic
features (lexical, morphosyntactic and semantic) for the task of
detecting threats of violence in a data set of YouTube comments. It
further examines the use of these features in combination with
different representations of the linguistic context. Our results show that ...
\end{abstract}

@@

Backoff: best of morphosyntactic and semantic?

@@

Held-out
